Bayesian hidden Markov model analysis of single-molecule force spectroscopy:\\ Characterizing kinetics under measurement uncertainty

### 2015-02-16 manuscripts/bayesian-hmm-method/bhmm.tex
Updated manuscript font to sans-serif. Updated Christian Kaiser affiliation.

\usepackage{palatino}
\usepackage{amsmath}
\usepackage{amssymb}

@@

%% TITLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Bayesian hidden Markov model analysis of single-molecule force spectroscopy: Characterizing kinetics under measurement uncertainty}
%\title{Characterizing the uncertainty in equilibrium kinetics from single-molecule force spectroscopy measurements using Bayesian hidden Markov models}
% JDC: Possible subtitle: Characterizing metastable states and transition rates under measurement uncertainty

@@

\author{Christian M.~Kaiser}
 \email{cmkaiser@berkeley.edu}
 \affiliation{California Institute of Quantitative Biosciences (QB3), University of California, Berkeley, CA 94720, USA}
 \affiliation{Department of Physics, University of California, Berkeley, CA 94720, USA}

>>>>

%\usepackage{palatino}
% Change to a sans serif font.
\usepackage{sourcesanspro}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}
%\usepackage[font=sf,justification=justified]{caption}
\usepackage[font=sf]{floatrow}

% Rework captions to use sans serif font.
\makeatletter
\renewcommand\@make@capt@title[2]{%
 \@ifx@empty\float@link{\@firstofone}{\expandafter\href\expandafter{\float@link}}%
  {\textbf{#1}}\sf\@caption@fignum@sep#2\quad
}%
\makeatother

\usepackage{amsmath}
\usepackage{amssymb}

@@

%% TITLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Bayesian hidden Markov model analysis of single-molecule force spectroscopy:\\
Characterizing kinetics under measurement uncertainty}
%\title{Characterizing the uncertainty in equilibrium kinetics from single-molecule force spectroscopy measurements using Bayesian hidden Markov models}
% JDC: Possible subtitle: Characterizing metastable states and transition rates under measurement uncertainty

@@

\author{Christian M.~Kaiser}
 %\email{cmkaiser@berkeley.edu}
 \email{kaiser.jhu.bio@gmail.com}
% \affiliation{California Institute of Quantitative Biosciences (QB3), University of California, Berkeley, CA 94720, USA}
 %\affiliation{Department of Physics, University of California, Berkeley, CA 94720, USA}
 \affiliation{Department of Biology, Krieger School of Arts and Sciences, Johns Hopkins University, Baltimore, MD 21218}
